---
title: ""
output: 
  html_document: 
    fig_height: 5
    fig_width: 5
---

```{r, include=FALSE}
library(DT)
library(scholar)
library(dplyr)
library(ggplot2)
library(plotly)
library(ggthemes)
theme_set(theme_base(base_size = 12) + theme(plot.background = element_rect(color = NA)))
id <- "DmQLj7gAAAAJ" # my id.
```

<br>
```{r, echo=FALSE}
p <- get_profile(id)
```

## List of publications

You can find here a list of my publications, sort them by column and filter them using the search box. Compared to the information shown in [my Google Scholar site](https://scholar.google.co.jp/citations?user=DmQLj7gAAAAJ&hl=en), only articles with more than one citation or published in the last two years are included.

```{r publications, echo=FALSE}
p <- get_publications(id)
current_year <- as.numeric(format(Sys.time(), "%Y"))
valid_year <- current_year - 2
pt <- p %>% filter(cites > 1 | year > valid_year) %>% select(year, cites, title, journal, author) %>% arrange(desc(year))
datatable(pt, rownames = FALSE)
```
<br>

## Citations per year

This plot shows my citation history per year.

```{r citations, echo=FALSE}
cit <- get_citation_history(id)
cit$year <- factor(cit$year)
g <- ggplot(cit, aes(x = year, y = cites)) + geom_bar(stat = "identity") + labs(y = "count")
p <- ggplotly(g)
p$x$config$displayModeBar <- 0
p
```

<br>

## Acknowledment

The information shown here is generated using the <a href="https://github.com/jkeirstead/scholar" target="_blank">scholar</a> R package to programmatically extract and analyze [Google Scholar](http://scholar.google.com) profiles. The interactive plot was generated using the [plotly](https://cran.r-project.org/package=plotly) R package.
